### 2015-08-26 LaTeX/RhodiumEmp.tex
stuff

We will eschew discussing the controls since the primary purpose of this analysis is to determine a baseline effect for civil war. Additionally, for the sake of space we do not show the full results from this regression, but they are available in section \ref{tab:baseline} of the Appendix. The key result pertains to the civil war variable for which we estimate a regression coefficient of approximately -2.568 with a standard error of 0.502.

@@

The analysis here highlights that there is little distinguishable difference in the expected values of GDP growth as a function of whether or not there a country was experiencing a civil war in the previous year. We argue that this is because the effect of civil conflict on economic growth becomes particularly relevant when that conflict is proximate to economic points of interest such as capital cities and major urban centers.

\section{Results}
\label{findings}

>>>>

We will eschew discussing the controls since the primary purpose of this analysis is to determine a baseline effect for civil war. Additionally, for the sake of space we do not show the full results from this regression, but they are available in section \ref{tab:baseline} of the Appendix. The key result pertains to the civil war variable for which we estimate a regression coefficient of approximately -2.568 with a standard error of 0.502.\footnote{This estimate corresponds closely to the result found by \citet{collier:1999}.}

@@

The analysis here highlights that, while there is a noticeable substantive difference in the expected GDP growth of civil war and non-civil war countries, there is also a large amount of inferential uncertainty in these estimates. We argue that this is because the effect of civil conflict on economic growth becomes particularly relevant when that conflict is proximate to economic points of interest such as capital cities and major urban centers. In other words, the heterogeneity of civil war leads to a diversity of economic outcomes for affected states.
%
\section{Results}
\label{findings}

### 2015-08-26 LaTeX/RhodiumTheory.tex
stuff

Nigeria and Cameroon have battled Boko Haram in a bloody conflict in their rural northern regions for half a decade. For the period between 2009 and 2013, the National Consortium for the Study of Terrorism and Responses to Terrorism (START) described Boko Haram as ``among the deadliest [terrorist groups] in the world'' \citep{pate:etal:2014}. The group's tactics range from car and suicide bombings to direct assaults to mass kidnappings. Nonetheless, Nigeria and Cameroon have both maintained strong economic growth during this period. The African Development Bank Group (AFDB) described Nigeria's economic growth from 2004 to 2014 as ``robust'' and projected ``moderate'' growth of 5\% for 2015 \citep{afdb:nigeria:2015}. On Cameroon, the AFDB said ``despite the security and humanitarian crisis in the region, Cameroonian growth remains strong at above 5\%'' \citep{afdb:cameroon:2015}.

>>>>

Nigeria and Cameroon have battled Boko Haram in a bloody conflict in their rural northern regions for half a decade. For the period between 2009 and 2013, the National Consortium for the Study of Terrorism and Responses to Terrorism (START) described Boko Haram as ``among the deadliest [terrorist groups] in the world'' \citep{pate:etal:2014}. The group's tactics range from car and suicide bombings to direct assaults to mass kidnappings. Nonetheless, Nigeria and Cameroon have both maintained strong economic growth during this period. The African Development Bank Group (AFDB) described Nigeria's economic growth from 2004 to 2014 as ``robust'' and projected ``moderate'' growth of 5\% for 2015 (AFDB "Nigeria" 2015)\nocite{afdb:nigeria:2015}. On Cameroon, the AFDB said ``despite the security and humanitarian crisis in the region, Cameroonian growth remains strong at above 5\%'' (AFDB "Cameroon" 2015) \nocite{afdb:cameroon:2015}.
